How to Write Theses\\ With Two Line Titles

### 2019-08-25 chapters/litReview/metamorphicTesting.tex
Updates from Overleaf

In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test. It is almost impossible to generate all the possible combinations of test cases to completely test a program which is why a lot of research is being conducted to develop more error-revealing test case selection strategies. A test case is called error-revealing if it is able to detect an error in the software otherwise it is labeled successful. Successful test case are the cases for which the program successfully computes the correct output. Since these test cases do not reveal any error, they are considered less important and are often not investigated further or, set aside for regression testing. {Zhou et al. (Metamorphic Testing and Its Applications ∗ † Zhi Quan Zhou‡∥, D.H. Huang‡, T.H. Tse§, Zongyuan Yang ¶, Haitao Huang ¶, and T. Y. Chen ‡)(Metamorphic testing and beyond) }

Chen, Cheung, and Yiu (1998) first introduced the idea of metamorphic testing to make use of valuable information in successful test cases in order to answer the oracle problem. Metamorphic testing reuses successful test cases to generate followup test cases according to metamorphic relations whose output can easily be predicted. A metamorphic relation(MR) is an expected relation among input and outputs of multiple executions of the target program(Metamorphic testing and beyond)(METRIC: METamorphic Relation Identification based on the Category - choice framework). To formally define MRs we can assume a function $f$ which produces the output $f(x)$ on input $x$. The MRs of the function can then be used to generate a transformation function $t$, which, when applied to input $x$ produces $t(x)$. This transformed input can then be run through the function $f$ and the transformation allows us to predict the value of $f(t(x))$(Automatic system testing of programs without test oracle). 
A simple example of a MR would be a program that calculates mean of a set of numbers. Certain transformations of the set of numbers will result in the same value for mean like: permuting the order of numbers, since, this neither changes the number of elements in the set nor the value of any element. Another transformation that can be used would be multiplying each number in the set with -1. The new mean will be the negative value of the previous mean.

System under test(SUT)

\subsection{Properties of a good metamorphic relation}
Segura et al. did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer important research questions about origin, current state, and, future of metamorphic testing. They identified that the most popular use of metamorphic testing was in web services, followed by computer graphics, simulation and modelling, and, embedded systems. They also found some other domains of application like financial software, optimization programs, and encryption programs.

They first studied the properties of effective metamorphic relations. To select the most effective metamorphic relations to detect faults one must have.
\begin{itemize}
	\item A good understanding of the problem domain since good metamorphic relations are usually strongly inspired by the semantics of the program under test.
	\item Metamorphic relations that make execution of the follow-up test case as different as possible from the source test case.
	\item Metamorphic relations derived from specific parts of the system since they are more effective than those targeting the whole system.
	\item Formally described metamorphic relations. In particular, a metamorphic relation should be a 3-tuple composed of $i)$ relation between the inputs of the source and follow-up test cases, $ii)$ relation between the outputs of source and follow-up test cases, and $iii)$ program function.
\end{itemize}

It should be noted that MT does not check the correctness of individual outputs. Instead, it checks the relations among several executions. Since no manual output predictions and comparisons are required, MT can be efficient and fully automated. \cite{Segura2016} The execution of a metamorphic test case is typically performed in two steps. First, a follow-up test case is generated by applying a transformation to the inputs of a source test case. Second, source and follow-up test cases are executed, checking whether their outputs violate the metamorphic relation. \par
	\subsection{Automatic System Testing of Programs without Test Oracles \cite{Murphy2009}}
	A number of frameworks have been developed to automate the process of metamorphic testing. Gotlieb and Botella \cite{Gotlieb2003} presented a framework called Automated Metamorphic Testing (AMT) to automatically generate test data for metamorphic relations. Given the source code of a program written in C and a metamorphic relation, AMT tries to find test cases that violate the relation. The underlying method is based on the translation of the code into an equivalent constraint logic program over finite domains. Other techniques like “special values” and random testing can also be used as source test cases for metamorphic testing. Genetic algorithms have also been used for the selection of source test cases, to maximize the paths traversed in the program under test.

		In this paper the authors have demonstrated the usefulness of metamorphic testing in assessing the quality of applications without test oracles. Comparing the outputs of the morphed data still remains a challenge especially if the data set is large or not in human readable format. The authors presented an approach called ``Automated Metamorphic System Testing'' to automate the metamorphic testing by considering the system as a blackbox and checking if the metamorphic properties holds after execution of the system. They also present another approach “Heuristic Metamorphic Testing” to reduce false positives and address some non-determinism. Unlike in the previous papers, here, the authors are focusing to improve the metamorphic testing technique itself. They list some benefits of using metamorphic testing: it can be used on broader domain of applications that display metamorphic properties, and it treats the application under test as a black box and does not require detailed understanding of the source code. \cite{Murphy2009}

		\cite{Segura2016} Iterative Metamorphic Testing (IMT) can be used to systematically exploit more information from metamorphic tests, by applying metamorphic relations iteratively. In IMT, a sequence of metamorphic relations is applied in a chain style, by reusing the follow-up test case of each metamorphic relation as the source test case of the next metamorphic relation. \par
		Murphy et al. \cite{Murphy2009} presented a framework named Amsterdam for the automated application of metamorphic testing. The tool takes as inputs the program under test and a set of metamorphic relations, defined in an XML file. Then, Amsterdam automatically runs the program, applies the metamorphic relations and checks the results.

		Automated Metamorphic System Testing: This technique can be used to test the application in development environment as well as in production as long as the users are only provided the output from the original execution and not the result from transformed input. In this model $i)$ Metamorphic properties are specified by the tester and applied to the input. $ii)$ The original input is fed into the application which is treated as a black-box and a transformation of the input is also generated. $iii)$ That transformed input is fed into a separate instance of the application running in a separate sandbox. $iv)$ When the invocations are finished, the results are compared and if they do not match according to the specifications, there is an error.
		Tester need not write any code and only needs to specify the metamorphic properties. They don't need to know the source code or other implementation details.
		Amsterdam framework: The metamorphic properties are specified using XML file. The specification consists of three parts: $i)$ how to transform the input, $ii)$ how to execute the program, and, $iii)$ how to compare the outputs.\par
		Heuristic Metamorphic testing: This method allows for small differences in outputs, in a meaningful way according to the application being used to address the problems of false positives and non-determinism. Imprecision in floating point calculation and representation of irrational number such as may result in failure of metamorphic testing even if the implementation is correct. If two outputs are close enough they are considered the same. The definition of close enough depends on the application and in complex applications checking semantic similarity may also be required.\cite{Murphy2009}

Although metamorphic testing presents a lot of opportunities to expand on the existing testing processes, they also have some limitations. They then list some of the limitations of using metamorphic testing: \cite{Murphy2009}
		\begin{itemize}
			\item	Manual transformation of large input data can be laborious and error-prone. They need special tools to transform the input.
			\item Comparing the outputs(some of which may be very large and/or in not human-readable format) of the input data can be tedious.
			\item Floating point calculations can also lead to imprecision even though the calculations are programmatically correct.
			\item Coming up with the initial test-cases is also a challenge as some defects may only occur under certain inputs.
		\end{itemize}

		Some of the research challenges identified by the authors are:{A Survey on Metamorphic Testing \cite{Segura2016}}
		\begin{itemize}
			\item Lack of guidelines, with step-by-step process to guide testers, experts, and beginners, in the construction of good metamorphic relations.
			\item Prioritisation and minimisation of metamorphic relations: It is worth mentioning that test case minimisation is a NP-hard problem and therefore heuristic techniques should be explored.
			\item Generation of likely metamorphic relations.
			\item Combination of metamorphic relations.
			\item Automated generation of best possible source test cases.
			\item Lack of metamorphic testing tools.
		\end{itemize}

>>>>

In the absence of a reliable oracle to indicate the correct output for arbitrary inputs, machine learning programs are often very hard to test. It is almost impossible to generate all the possible combinations of test cases to completely test a program. Thus, a lot of research is being conducted to develop more error-revealing test case selection strategies. A test case is called error-revealing if it is able to detect an error in the software otherwise it is labeled successful. Successful test case are the cases for which the program successfully computes the correct output. Since these test cases do not reveal any error, they are considered less important and are often not investigated further or, set aside for regression testing \cite{Zhou2004, Chen2003}.

Chen, Cheung, and Yiu \cite{Chen1998} first introduced the idea of metamorphic testing to make use of valuable information in successful test cases in order to answer the oracle problem. Metamorphic testing reuses successful test cases to generate followup test cases according to metamorphic relations. Thus, rather being a test selection strategy, metamorphic testing is used to generate new test cases whose output can easily be predicted \cite{Murphy2008}. A metamorphic relation(MR) is an expected relation among input and outputs of multiple executions of the target program \cite{Chen2003,Zhou2016}. Consider a function $f$ which produces the output $f(x)$ on input $x$. The metamorphic relations of the function can then be used to generate a transformation function $t$, which, when applied to input $x$ produces $t(x)$. The transformed input $t(x)$ can then be run through the function $f$ to generate the output $f(t(x))$. This $f(t(x))$ is then compared to the expected behaviour of $f$ on $t(x)$ from the metamorphic relation to find any error. \cite{Murphy2009}. 
To demonstrate a MR, consider a program that calculates the mean of a set of real numbers. Certain transformations of the input numbers will result in the same value for mean. An example of this transformation can be a permutation of the order of input. Since, this does not changes the number of elements in the input set or the value of any element, we can safely assume that the mean will remain same. Another transformation could be to multiply each number in the input set with -1. The new mean will be the negative value of the previous mean. In both the cases we can easily predict the output for the newly generated test cases. Thus, multiplication and permutation are metamorphic relations for this algorithm.

\subsection{Properties of a good metamorphic relation}
Segura et al. \cite{Segura2016} did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer important research questions about origin, current state, and, future of metamorphic testing. They identified that the most popular use of metamorphic testing was in web services, followed by computer graphics, simulation and modelling, and, embedded systems. They also found some other domains of application like financial software, optimization programs, and encryption programs.

They also studied the properties of effective metamorphic relations. To select the most effective metamorphic relations to detect faults one must have.
\begin{itemize}
	\item A good understanding of the problem domain since good metamorphic relations are usually strongly inspired by the semantics of the program under test.
	\item Metamorphic relations that make execution of the follow-up test case as different as possible from the source test case.
	\item Metamorphic relations derived from specific parts of the system since they are more effective than those targeting the whole system.
	\item Formally described metamorphic relations. In particular, a metamorphic relation should be a 3-tuple composed of $i)$ relation between the inputs of the source and follow-up test cases, $ii)$ relation between the outputs of source and follow-up test cases, and $iii)$ program function.
\end{itemize}
Research from Chen et al. shows that metamorphic relations that makes the subsequent execution the most different from the initial execution have the best chances of revealing failure. Although, they did not explicitly define what is meant by "different" in terms of multiple execution \cite{Chen2003}.

The execution of a metamorphic test case is typically performed in two steps. First, a follow-up test case is generated by applying a transformation to the inputs of a source test case. Second, source and follow-up test cases are executed, checking whether their outputs violate the metamorphic relation. It should be noted that MT does not check the correctness of individual outputs. Instead, it checks the relations among several executions. Since no manual output predictions and comparisons are required, MT can be efficient and fully automated \cite{Segura2016}. Comparing the outputs of the morphed data still remains a challenge especially if the data set is large or not in human readable format.
% 	\subsection{Automatic System Testing of Programs without Test Oracles \cite{Murphy2009}}
A number of frameworks have been developed to address this issue and automate the process of metamorphic testing. Gotlieb and Botella \cite{Gotlieb2003} presented a framework called Automated Metamorphic Testing (AMT) to automatically generate test data for metamorphic relations. Given the source code of a program written in C and a metamorphic relation, AMT tries to find test cases that violate the relation. The underlying method is based on the translation of the code into an equivalent constraint logic program over finite domains. Other techniques like “special values” and random testing can also be used as source test cases for metamorphic testing. Genetic algorithms have also been used for the selection of source test cases, to maximize the paths traversed in the program under test. But, their focus was on generation of new test cases and not on verifying that the metamorphic properties hold after execution.

Murphy et al. \cite{Murphy2009} also demonstrated how metamorphic testing can be used to assess the quality of applications without test oracles.  They presented an approach called ``Automated Metamorphic System Testing'' to automate the metamorphic testing by considering the system as a black box and checking if the metamorphic properties holds after multiple executions of the system. In this model $i)$ Metamorphic properties are specified by the tester and applied to the input. $ii)$ A transformation of the input is also generated and the original input is fed into the application. $iii)$ The transformed input is fed into a separate instance of the application running in a separate sandbox. $iv)$ When the invocations are finished, the results are compared and if they do not match according to the specifications, there is an error. All a tester has to do is provide the metamorphic properties and does not require the knowledge of implementation.

In order to demonstrate Automated Metamorphic System Testing they created a framework called Amsterdam. The tool takes as inputs the program under test and a set of metamorphic relations, defined in an XML file. The XML specification consists of three parts: $i)$ how to transform the input, $ii)$ how to execute the program, and, $iii)$ how to compare the outputs. Then, Amsterdam automatically runs the program, applies the metamorphic relations and checks the results.

While implementing Amsterdam framework, it became quite clear that small deviations in results calculations (like floating point operations) could cause a problem where exact results were expected. Also, many applications implements non-determinism for which outputs cannot be reliably predicted, hence, rendering metamorphic testing ineffective. To address this, they introduce a technique called "Heuristic Metamorphic Testing", based on the concept of "heuristic test oracles". Heuristic Metamorphic Testing reduces false positives and addresses non-determinism by allowing for small differences in outputs, in a meaningful way according to the application being used. If two outputs are close enough they are considered the same. The definition of close enough depends on the application and in complex applications checking semantic similarity may also be required. This approach also treats applications under test as black boxes and do not require detailed understanding of source code.

Although metamorphic testing presents a lot of opportunities to expand on the existing testing processes, they also have some limitations. Murphy, et al. \cite{Murphy2009} list some of the limitations of using metamorphic testing:
\begin{itemize}
	\item Manual transformation of large input data can be laborious and error-prone. They need special tools to transform the input.
	\item Comparing the outputs(some of which may be very large and/or in not human-readable format) of the input data can be tedious.
	\item Floating point calculations can also lead to imprecision even though the calculations are programmatically correct.
	\item Coming up with the initial test-cases is also a challenge as some defects may only occur under certain inputs.
\end{itemize}

Segura, et al. \cite{Segura2016} also identified some research challenges:
\begin{itemize}
	\item Lack of guidelines, with step-by-step process to guide testers, experts, and beginners, in the construction of good metamorphic relations.
	\item Prioritization and minimization of metamorphic relations: It is worth mentioning that test case minimization is a NP-hard problem and therefore heuristic techniques should be explored.
	\item Generation of likely metamorphic relations.
	\item Combination of metamorphic relations.
	\item Automated generation of best possible source test cases.
	\item Lack of metamorphic testing tools.
\end{itemize}

### 2019-08-25 chapters/litReview/mlAlgo.tex
Updates from Overleaf

\section{Overview of Machine Learning Algorithms}
\subsection{Supervised Sequence Labelling with Recurrent Neural Networks \cite{Graves}}
Artificial neural networks (ANNs) were originally developed as mathematical models of the information processing capabilities of biological brains. Although it is now clear that ANNs bear little resemblance to real biological neurons, they enjoy continuing popularity as pattern classifiers. The basic structure of an ANN is a network of small processing units, or nodes, joined to each other by weighted connections. In terms of the original biological model, the nodes represent neurons, and the connection weights represent the strength of the synapses between the neurons. The network is activated by providing an input to some or all of the nodes, and this activation then spreads throughout the network along the weighted connections. ANNs without cycles are referred to as feedforward neural networks (FNNs). Well known examples of FNNs include perceptrons, radial basis function networks, Kohonen maps and Hopfield nets. The most widely used form of FNN is the multilayer perceptron(MLP). It has been proven that an MLP with a single hidden layer containing a sufficient number of nonlinear units can approximate any continuous function on a compact input domain to arbitrary precision. For this reason MLPs are said to be universal function approximators.
At each unit in a layer the activation function $\theta_h$ is applied, yielding the final activation $b_h$ of the unit. The most common choices for neural network activation function are the hyperbolic tangent and the logistic sigmoid. An important feature of both tanh and the logistic sigmoid is their nonlinearity. Nonlinear neural networks are more powerful than linear ones since they can, for example, find nonlinear classification boundaries and model nonlinear equations. Another key property is that both functions are differentiable, which allows the network to be trained with gradient descent. Because of the way they reduce an infinite input domain to a finite output range, neural network activation functions are sometimes referred to as squashing functions. The output vector $y$ of an MLP is given by the activation of the units in the output layer. The network input $a_k$ to each output unit $k$ is calculated by summing over the units connected to it, exactly as for a hidden unit. Both the number of units in the output layer and the choice of output activation function depend on the task the network is applied to. For classification problems with $K > 2$ classes, the convention is to have $K$ output units, and normalise the output activations with the softmax function to obtain the class probabilities which is also known as a multinomial logit model.

>>>>

\section{Overview of Machine Learning Algorithms}
\subsection{Neural network}
Neural networks were first introduced in 1944 by two University of Chicago researchers Warren McCullough and Walter Pitts, who later moved to MIT in 1952. These algorithms are modeled loosely after the human brain, that are designed to recognize patterns.  Dr. Robert Hecht-Nielsen, inventor of the first neurocomputer defines a neural network as:
"...a computing system made up of a number of simple, highly interconnected processing elements, which process information by their dynamic state response to external inputs"\cite{Caudill}.
\begin{figure}[htb!]
    \centering
    \includegraphics[scale=0.15]{files/nn.png}
    \caption{Neural network}
    \label{Neural network}
    \end{figure}
    \FloatBarrier
% cite figure: https://towardsdatascience.com/applied-deep-learning-part-1-artificial-neural-networks-d7834f67a4f6
A typical neural network looks like a variation of Figure 2.1. \\
Input layer: The leftmost layer in the network is made up of input neurons and the layer is called the input layer. There is no computation performed in the nodes at this layer. Input layer simply provides the information from the environment to the next layer.
Hidden layers: The layers in the middle make up the hidden layers, as the neurons in these layers are neither inputs nor outputs. There can be zero or multiple hidden layers. Hidden layers takes the input from the input layer and passes information to the output layer after performing computation on the data. 
Output layer: The rightmost or output layer contains the output neurons, or, as in this case, a single output neuron. 
There are no set rules to design the layers of a neural network (specially the hidden layers) and this process is often considered as an art\cite{NN}. We determine the number of hidden layers and nodes empirically for each particular case in order to optimize performance. The edges (or connections) between a layer and the layer before it are represented by a weight $\omega_{ij}$, which represents the strength of connection between i and j nodes. During the training phase of the neural network, we assign random values to the weights for each connection. The algorithm then tries to optimize the weights so that the error function is minimized. For each node at a layer all the output from the previous node is multiplied by the weight of connections between them and the sum of all the different connections produces the value at that node. This cycle is repeated for all the nodes in every layer. The algorithm compares the prediction from the output layer to the real value and readjusts the weights. Once the optimal value is reached the network can be used to make predictions\cite{hall199}.

These neural networks where the output from one layer is used as input to the next layer are called feedforward neural networks\cite{NN}\cite{hall199}. There are no loops in the feedforward neural network and the information flows in one direction and are never fed back. The most well known form of a feed forward neural network is called multilayer perceptron(MLP). MLPs are also called universal function approximator. A single hidden layer MLP with a sufficient number of nonlinear units can act as a continuous function on to a narrow input domain with arbitrary precision. \cite{Graves}.
There are some other models of artificial neural networks in which feedback loops are possible. These models are called recurrent neural networks. The idea in these models is to have neurons which fire for some limited duration of time, before becoming quiescent. That firing can stimulate other neurons, which may fire a little while later, also for a limited duration. That causes still more neurons to fire, and so over time we get a cascade of neurons firing. Loops don't cause problems in such a model, since a neuron's output only affects its input at some later time, not instantaneously. Recurrent neural nets have been less influential than feedforward networks, in part because the learning algorithms for recurrent nets are (at least to date) less powerful. But recurrent networks are still extremely interesting. They're much closer in spirit to how our brains work than feedforward networks. And it's possible that recurrent networks can solve important problems which can only be solved with great difficulty by feedforward networks.\cite{NN} % cite: http://neuralnetworksanddeeplearning.com/chap1.html

\subsection{Convolutional neural network}
Convolutional neural networks (ConvNet) are very similar to ordinary neural networks in structure. They work by extracting simple features at a higher resolution and then converting them into more complex features at a coarser resolution \cite{simard2003best}. It does so by performing dot product on the inputs received at each neuron and optionally follow it with non-linearity. Just like a normal neural network, convolutional neural network (from the input image to output class) can be expressed as a single differential function. It also has a loss function on the fully-connected output layer.

Convolutional Neural Networks (ConvNet) are very similar to ordinary Neural Networks. they are made up of neurons that have learnable weights and biases. Each neuron receives some inputs, performs a dot product and optionally follows it with a non-linearity. The whole network still expresses a single differentiable score function: from the raw image pixels on one end to class scores at the other. And they still have a loss function (e.g. SVM/Softmax) on the last (fully-connected) layer and all the tips/tricks we developed for learning regular Neural Networks still apply. 
What makes it different is that ConvNet architectures make the explicit assumption that the inputs are images, which allows us to encode certain properties into the architecture. These then make the forward function more efficient to implement and vastly reduce the amount of parameters in the network. Convolutional Neural Networks take advantage of the fact that the input consists of images and they constrain the architecture in a more sensible way. In particular, unlike a regular Neural Network, the layers of a ConvNet have neurons arranged in 3 dimensions: width, height, depth. (Note that the word depth here refers to the third dimension of an activation volume, not to the depth of a full Neural Network, which can refer to the total number of layers in a network). 
A ConvNet architecture is made up of the following layers: \\
Input: This layer holds the raw input image in form of it's pixel values and color channels.\\
Convolutional layer: This layer computes the dot product between it's weight and a small region in the previous layer it is connected to.\\
Rectified linear unit: \\
Fully connected layer: The fully connected output layer computes the class scores for the input. The neurons in this layer are connected to every neuron in the last layer.\\

A simple ConvNet is a sequence of layers, and every layer of a ConvNet transforms one volume of activations to another through a differentiable function. We use three main types of layers to build ConvNet architectures: Convolutional Layer, Pooling Layer, and Fully-Connected Layer (exactly as seen in regular Neural Networks). We will stack these layers to form a full ConvNet architecture.

RELU layer will apply an elementwise activation function, such as the $max(0,x)$ thresholding at zero. This leaves the size of the volume unchanged ([32x32x12]).
POOL layer will perform a downsampling operation along the spatial dimensions (width, height), resulting in volume such as [16x16x12].
FC (i.e. fully-connected) layer will compute the class scores, resulting in volume of size [1x1x10], where each of the 10 numbers correspond to a class score, such as among the 10 categories of CIFAR-10. As with ordinary Neural Networks and as the name implies, each neuron in this layer will be connected to all the numbers in the previous volume.
\begin{figure}[htb!]
    \centering
    \includegraphics[scale=1.25]{chapters/litReview/files/convNet.png}
    \caption{Convolutional Neural network \cite{convNN}}
    \label{Neural network}
    \end{figure}
    \FloatBarrier

Note that some layers contain parameters and other don’t. In particular, the CONV/FC layers perform transformations that are a function of not only the activations in the input volume, but also of the parameters (the weights and biases of the neurons). On the other hand, the RELU/POOL layers will implement a fixed function. The parameters in the CONV/FC layers will be trained with gradient descent so that the class scores that the ConvNet computes are consistent with the labels in the training set for each image.
%cite http://cs231n.github.io/convolutional-networks/

\subsection{Naive Bayes}
In it's simplest form a Naive Bayes algorithm is a type of Bayesian network where all attributes are independent given the value of the class variable. This property is called conditional independence. It is obvious that the conditional independence assumption is rarely true in most real-world applications\cite{zhang2004optimality}. Despite this limitation the algorithm is very popular and works quite well in many real-world situations like document classification and spam filtering. The classifier is a really common supervised learning algorithm because it is fast, easy to implement and relatively effective. They also require relatively small number of training data to estimate the necessary parameters of the network\cite{scikit-learn}. Given a class variable $y$ and dependent feature vector $x_{1}$...$x_{n}$, Bayes theorem states that:
\begin{center}
    $P(y|x_{1},...,x_{n}) = \frac{P(y)P(x_{1},...,x_{n}|y)}{P(x_{1},...,x_{n})}$
\end{center}
From the conditional independence of features, and, value of a class we know that: 
\begin{center}
$P(y \mid x_1, \dots, x_n) = \frac{P(y) \prod_{i=1}^{n} P(x_i \mid y)}
                                 {P(x_1, \dots, x_n)}$
\end{center}
% Include the equations from https://scikit-learn.org/stable/modules/naive_bayes.html
For a given input $P(x_{1},...,x_{n})$ is constant. Therefore 
\begin{center}
$P(y \mid x_1, \dots, x_n) \propto P(y) \prod_{i=1}^{n} P(x_i \mid y)$
\end{center}
And an expected classification $\hat{y}$ can be obtained by:
\begin{center}
$\hat{y} = \arg\max_y P(y) \prod_{i=1}^{n} P(x_i \mid y)$
\end{center}
The main distinction between different versions of naive Bayes classifiers are the assumptions they make about the distribution of $P(x_i \mid y)$\cite{scikit-learn}. The multinomial Naive Bayes suffers from a systematic problem of assigning poor weights to necessary parameters if once class has more training examples than others. This effect lowers the weights for classes with less training examples\cite{rennie2003tackling}. For this reason we have equal numbers of training and testing examples for each class in our experiment.

\subsection{k-Nearest Neighbor}
The nearest neighbor classifier is a supervised classification technique which assigns an input sample vector (whose classification is to be predicted) to the class of it's nearest neighbors. The similarity between the input and the neighbors is calculated based on some distance metrics. This process does not require any pre-processing of the labeled set of neighbors before their use \cite{cover1967}. This idea can be further extended to assign the class of input variable to the class represented by majority of the $k$ nearest neighbors, where $k$ is a positive number specified by the user. The optimal value of $k$ depends on the data. A larger value of $k$ makes the classification boundaries less distinct while suppressing the noise effect \cite{scikit-learn}. One problem with implementing $k$ nearest algorithm is that in some cases there may be a tie among classes between the $k$ neighbors. This problem can be solved by restricting the values of $k$. In a binary classification problem, the values of $k$ can be restricted to odd numbers so that ties can be avoided. In a multi-class classification, this can be resolved by assigning the input to the class for which the sum of distance to each neighbor is the least. This could further lead to a tie and in that case an arbitrary assignment can be made \cite{keller1985}.
\begin{figure}[htb!]
    \centering
    \includegraphics[scale=1]{files/knn.png}
    \caption{$k$-Nearest neighbor}
    \label{k-Nearest neighbor}
    \end{figure}
    \FloatBarrier

\cite{cover1967}
A set of n pairs is given $(x1,\theta 2),...(xn,\theta n)$ s.t the x′is take value in a metric space X upon which is defined a metric d.
The category $\theta$ i is assigned to the ith sample or individual from finite subset {1,2, ... M} and xi is the measurement made upon that ith.
we shall say ”xi belongs to $\theta$ i” when we mean precisely that the ith sample have measurement xi with category $\theta i$ .
Our Goal is to classify the measurement x , for a new arriving pair $(x,\theta )$, the classification is procedure to estimate the $\theta$  since x is observable .
The estimation of $\theta$  is done by utilizing the fact that we have set of n correctly classified points.
We shall call : nearest neighbor of x if
'xn ∈(x1,x2,x3,....xn)'
min d(xi,x) = d(xn,x) i = 1,2,3...,n.

In this case the decision of the nearest neighbor rule is assigning the category $\theta$ n to our new measurement x .
The 1-NN rule decide x belongs to the category of nearest neighbor and ignored the others!.
In general k-NN rule decide x belongs to the category of majority vote of the nearest k neighbors.

\subsection{Support vector machine}
A support vector machine (SVM)  is a supervised machine learning classifier. The support vectors lie on the dotted hyperplanes parallel to the separating hyperplane. The margin, the minimum gap between the supporting hyperplane and the separating hyperplane, is chosen to be maximum. The pseudo-code is a common, abstract description of implemented SMO computer programs. Because SMO is an algorithm for solving the SVM optimization problem, it corresponds to the model constructor and is an abstract version of the quasi-testable core.\cite{Nakajima2016}

support vector machines (SVMs), based on statistical learning theory, are gaining applications in the areas of machine learning, computer vision and pattern recognition because of high accuracy and good generalisation capability

Based on the structural risk minimization (SRM) principal, SVM can get decision-making rules and achieve small error for independent tests set and hence can solve the learning problems efficiently \cite{svm2008}. Recently SVM is applied to solve the problems such as nonlinear, local minimum and high dimension. In many practical applications, SVM can ensure higher accuracy for a long-term prediction compared to other computational approaches.
SVM is based on the concept of decision planes that define decision boundaries. SVM creates a hyperplane by using a linear model to implement nonlinear class boundaries through some nonlinear mapping input vectors into a high-dimensional feature space \cite{SAMANTA2003657}

It aims to create a decision boundary between two classes that enables the prediction of labels from one or more feature vectors (6). This decision boundary, known as the hyperplane, is orientated in such a way that it is as far as possible from the closest data points from each of the classes. These closest points are called support vectors.
The most obvious drawback to the SVM algo- rithm, as described thus far, is that it apparently only handles binary classification problems. 
Generalizing to multiclass clas- sification is straightforward and can be accom- plished by using any of a variety of methods. To recognize three classes, A, B and C, we simply have to train three separate SVMs to answer the binary questions, “Is it A?,” “Is it B?” and “Is it C?”. More sophisti- cated approaches also exist, which generalize the SVM optimization algorithm to account for multiple classes. \cite{noble2006support}
The SVM algorithm was originally proposed to construct a linear classifier in 1963 by Vapnik (7). An alternative use for SVM is the kernel method, which enables us to model higher dimensional, non-linear models (8). In a non-linear problem, a kernel function could be used to add additional dimensions to the raw data and thus make it a linear problem in the resulting higher dimensional space (Figure 2). Briefly, a kernel function could help do certain calculations faster which would otherwise would need computations in high dimensional space.
It is defined as:

K (x, y)=<f(x), f(y)>

Here K is the kernel function, x, y are n dimensional inputs. f is used to map the input from n dimensional to m dimensional space. <x, y> denotes the dot product. With kernel functions, we could calculate the scalar product between two data points in a higher dimensional space without explicitly calculating the mapping from the input space to the higher dimensional space. In many cases, computing the kernel is easy while going to the high dimensional space to compute the inner product of two feature vectors is hard. The feature vector for even simple kernels can blow up in size, and for kernels like the Radial Basis Function (RBF) kernel (KRBF(x, y) = exp (-γ||x - y||2), the corresponding feature vector is infinite dimensional. Yet, computing the kernel is almost trivial.

The choice of kernel function among other factors could greatly affect the performance of an SVM model. However, there is no way to figure out which kernel would do the best for a specific pattern recognition problem. The only way to choose the best kernel is through trials. We can start with a simple SVM and then experiment with a variety of ‘standard’ kernel functions. Depending on the nature of the problem, it is possible that one kernel is better than the other kernels. An optimal kernel function can be selected from a fixed set of kernels in a statistically rigorous fashion by using cross-validation.

\begin{figure}[htb!]
    \centering
    \includegraphics[scale=0.75]{files/svm.png}
    \caption{SVM maximizes the margin between classes}
    \label{SVM maximizes the margin between classes}
    \end{figure}
    \FloatBarrier

### 2019-08-25 chapters/methodology/collection.tex
new
Updates from Overleaf

\section{Algorithm}
\subsection{Convolutional neural network}
\subsection{2-layer neural network}

@@

\begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/digit.png}
            \caption{Sample EMNIST-MNIST dataset}
            \label{fig:EMNIST MNIST dataset}
        \end{subfigure}%
        \label{fig:Rotate-misclassifications}
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/letter.png}
            \caption{Sample EMNIST-MNIST dataset}
            \label{fig:EMNIST MNIST dataset}
        \end{subfigure}%
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

>>>>

\section{Algorithm}
\subsection{Neural network}
 Each hidden layer is made up of a set of neurons, where each neuron is fully connected to all neurons in the previous layer, and where neurons in a single layer function completely independently and do not share any connections. If the image is a 64 by 64 greyscale image, then we'd have 4,096=64x64 input neurons, with the intensities scaled appropriately between 0 and 1. The output layer will contain just a single neuron, with output values of less than 0.5 indicating "input image is not a 9", and values greater than 0.5 indicating "input image is a 9 ". The input pixels are greyscale, with a value of 0.0 representing white, a value of 1.0 representing black, and in between values representing gradually darkening shades of grey. The second layer of the network is a hidden layer.

2 layer
\subsection{Convolutional neural network}
In EMNIST dataset, each image is single-channel of size 28 x 28 x 1.

\subsection{Naive Bayes}
What the function is 
Input and output

\subsection{k-Nearest Neighbor}
The 1-NN rule decide x belongs to the category of nearest neighbor and ignored the others!.
In general k-NN rule decide x belongs to the category of majority vote of the nearest k neighbors.

@@

\begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/digit.png}
            \caption{Sample EMNIST-MNIST dataset}
            \label{fig:EMNIST MNIST dataset}
        \end{subfigure}%
        \label{fig:Rotate-misclassifications}
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/letter.png}
            \caption{Sample EMNIST-Letter dataset}
            \label{fig:EMNIST MNIST dataset}
        \end{subfigure}%
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier
